Papers

### 2025-07-31 papers.qmd
update papers

## Accepted or In Press

- Calalo JA., Ngo T., Sullivan S., Strand K., Buggeln JH., Lokesh R., Roth A., Carter MJ., Kurtzer IL., & Cashaback JGA.. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*. ---
[{{< ai doi >}}](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank" style="color: inherit;"}

@@

>>>>

<!-- ## Accepted or In Press -->

@@

- Calalo JA., Ngo T., Sullivan S., Strand K., Buggeln JH., Lokesh R., Roth A., Carter MJ., Kurtzer IL., & Cashaback JGA.. (2025). Online movements reflect ongoing deliberation. *Journal of Neuroscience*. ---
[{{< ai doi >}}](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_calalo-etal_online-movements-reflect-ongoing-deliberation.pdf){target="_blank" style="color: inherit;"}
